---
title: "**Homework 4**"
author: "Shaliha Guarnera - SDS 315 - scg2595 - [GitHub Repository](https://github.com/shalihaguarnera/SDS315HW4)"
date: "February 2024"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```

```{r}

gasprices <- read.csv('gasprices.csv')
sclass <- read.csv('sclass.csv')
nbc <- read.csv('nbc_pilotsurvey.csv')
ebay <- read.csv('ebay.csv')
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(kableExtra)
library(dplyr)
library(rvest)
library(sas7bdat)
library(stringr)
library(lubridate)
library(reshape2)
library(htmltools)
library(mosaic)

```

\newpage

## **Problem 1: Gas Prices**

### **Part A**

```{r}

ggplot(gasprices) +
  geom_histogram(aes(x=Price, fill=Competitors), position='identity', alpha = 0.7) +
  labs(title = 'Frequency of Gas Prices by Presence of Competitors', x = 'Price ($)', y = 'Frequency', fill = 'Competitors') +
  scale_fill_manual(values = c('lightpink', 'lightblue'))

boot_diff_competitors <-  do(10000) * diffmean(Price ~ Competitors, data = mosaic::resample(gasprices))
competitors_confint <- confint(boot_diff_competitors, level = 0.95)

```

Claim: Gas stations charge more if they lack direct competition in sight. \
Evidence: The estimated mean difference between gas stations that lack direct competition in sight and gas stations that do have direct competition in sight is `r round(competitors_confint[6], 4)`, with a 95% confidence interval between `r round(competitors_confint[2], 4)` and `r round(competitors_confint[3], 4)`. Since the estimate is negative, on average, gas prices within gas stations that lack competitors are higher than gas stations with competitors. However, since the interval contains zero, the mean difference is thus not statistically significant at a 5% level. \
Conclusion: The theory is supported by the data.

### **Part B**

```{r}

gasprices$Income = gasprices$Income/100000

ggplot(gasprices) + 
  geom_point(aes(x = Income, y = Price), color = 'lightblue') +
  labs(title = 'Average Household Income of an Area and Gas Prices', x = 'Income', y = 'Prices')

boot_income_price <- do(10000) * lm(Price ~ Income, data = mosaic::resample(gasprices))
income_price_confint <- confint(boot_income_price, level = 0.95)

```

Claim: The richer the area, the higher the gas prices. \
Evidence: The relationship between average household income and gas prices in the are has a positive correlation with an estimated `r round(income_price_confint[2, 6], 4)` increase in gas price per $10,000 increase in household income. This change is represented in the 95% confidence interval between `r round(income_price_confint[2, 2], 4)` and `r round(income_price_confint[2, 3], 4)`. \
Conclusion: The theory is supported by the data.

### **Part C**

```{r}

ggplot(gasprices) +
  geom_histogram(aes(x = Price, fill = Stoplight), position = 'identity', alpha = 0.7) +
  labs(title = 'Frequency of Gas Prices by Presence of Stoplights', x = 'Price ($)', y = 'Frequency', fill = 'Stoplight') +
  scale_fill_manual(values = c('lightpink', 'lightblue'))

boot_diff_stoplight <- do(10000) * diffmean(Price ~ Stoplight, data = mosaic::resample(gasprices))
stoplight_confint <- confint(boot_diff_stoplight, level=0.95)

```

Claim: Gas stations at stoplights charge more. \
Evidence: The estimated mean difference between gas stations at stoplights and gas stations that are not at stoplights is `r round(stoplight_confint[6], 4)`, with a 95% confidence interval between `r round(stoplight_confint[2], 4)` and `r round(stoplight_confint[3], 4)`. Since the estimate is positive, on average, gas prices within gas stations at stoplights are higher than gas prices within gas stations that aren't at stoplights. However, since the interval contains zero, the mean difference is thus not statistically significant at a 5% level. \
Conclusion: The theory is supported by the data.


### **Part D**

```{r}

ggplot(gasprices) +
  geom_histogram(aes(x = Price, fill = Highway), position = 'identity', alpha = 0.7) +
  labs(title = 'Frequency of Gas Prices by Highway Access', x = 'Price ($)', y = 'Frequency', fill = 'Highway') +
  scale_fill_manual(values = c('lightpink', 'lightblue'))

boot_diff_highway <- do(10000) * diffmean(Price ~ Highway, data = mosaic::resample(gasprices))
highway_confint <- confint(boot_diff_highway, level=0.95)

```

Claim: Gas stations with direct highway access charge more. \
Evidence: The estimated mean difference between gas stations that have direct highway access and gas stations that do not have direct highway access is `r round(highway_confint[6], 4)`, with a 95% confidence interval between `r round(highway_confint[2], 4)` and `r round(highway_confint[3], 4)`. Since the estimate is positive, on average, gas prices within gas stations that have access to highways are higher than gas stations with without access to highways Since the interval does not contain zero, the mean difference is statistically significant at a 5% level. \
Conclusion: The theory is supported by the data.

### **Part E**

```{r}
gasprices <- gasprices %>%
  mutate(brand_shell = Brand == "Shell")

ggplot(gasprices) +
  geom_histogram(aes(x = Price, fill = brand_shell), position = 'identity', alpha = 0.7) +
  labs(title = 'Frequency of Gas Prices by Brand (Shell or Non-Shell)', x = 'Price ($)', y = 'Frequency', fill = 'brand_shell') +
  scale_fill_manual(values = c('lightpink', 'lightblue'))

boot_diff_brands <- do(10000) * diffmean(Price ~ brand_shell, data = mosaic::resample(gasprices))
shell_confint <- confint(boot_diff_brands, level=0.95)

```

Claim: Shell charges more than all other non-Shell brands. \
Evidence: The estimated mean difference between gas stations that are of the 'Shell' brand and gas stations that are not of the brand "Shell" is `r round(shell_confint[6], 4)`, with a 95% confidence interval between `r round(shell_confint[2], 4)` and `r round(shell_confint[3], 4)`. Since the estimate is negative, on average, gas prices at "Shell" gas stations are higher than gas stations that aren't "Shell". Since the interval does contain zero, the mean difference is thus not statistically significant at a 5% level. \
Conclusion: The theory is supported by the data.

\newpage

## **Problem 2: **

### **Part A**
```{r}

sclass_subset <- sclass %>%
  filter(year == 2011 & trim == '63 AMG')

prop_sclass_bootstrap <- do(10000) * mean(~mileage, data = resample(sclass_subset))
sclass_confint <- confint(prop_sclass_bootstrap, level=0.95)

```

The estimated average mileage of used 2011 S-Class 63 AMGs that were hitting the user-car market with 95% confidence is between `r round(sclass_confint[2], 2)` and `r round(sclass_confint[3], 2)`.

### **Part B**
```{r}

sclass_subset_2 <- sclass %>%
  filter(year == 2014 & trim == "550") %>%
  mutate(isBlack = color == 'Black')

prop_sclass_bootstrap_2 <- do(10000) * prop(~isBlack, data = resample(sclass_subset_2))
sclass_confint_2 <- confint(prop_sclass_bootstrap_2, level=0.95)

```

The estimated proportion of 2014 S-Class 550s that were painted black with 95% confidence is between `r round(sclass_confint_2[2], 2)` and `r round(sclass_confint_2[3], 2)`.

## **Problem 3: NBC**

### **Part A**

```{r}

nbc_ed_earl <- nbc %>%
  filter(Show == 'Living with Ed' | Show == 'My Name is Earl')

diff_nbc_bootstrap <- do(10000) * diffmean(Q1_Happy ~ Show, data = mosaic::resample(nbc_ed_earl))
nbc_confint <- confint(diff_nbc_bootstrap, level=0.95)

```

Question: Who makes people happier: Ed or Earl? \
Approach: In order to answer this question, I filtered the dataset to only contain observations that were from the shows 'Living with Ed' or 'My Name is Earl'. Next, I computed a bootstrap of the mean difference of 'Q1_Happy' responses between the two shows. I then computed a 95% confidence interval of the bootstrap. \
Results: The estimated mean difference of happiness ratings is `r round(nbc_confint[6], 4)` with a 95% confidence interval between `r round(nbc_confint[2], 4)` and `r round(nbc_confint[3], 4)`. \
Conclusion: Since the estimated mean difference is negative, on average, the show 'My Name is Earl' has a higher happiness rating in comparison to the show 'Living with Ed'. However, since the confidence interval contains zero, the mean difference is thus not statistically significant at a 5% level.

### **Part B**

```{r}

nbc_tbl_tala <- nbc %>%
  filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")

diff_nbc_bootstrap_2 <- do(10000) * diffmean(Q1_Annoyed ~ Show, data = mosaic::resample(nbc_tbl_tala))
nbc_tbl_tala_confint <- confint(diff_nbc_bootstrap_2, level=0.95)

```

Question: Which reality/contest show made people feel more annoyed? “The Biggest Loser” or “The Apprentice: Los Angeles.”? \
Approach: In order to answer this question, I filtered the dataset to only contain observations that were from the shows 'The Biggest Loser' or 'The Apprentice: Los Angeles'. Next, I computed a bootstrap of the mean difference of 'Q1_Annoyed' responses between the two shows. I then computed a 95% confidence interval of the bootstrap. \
Results: The estimated mean difference of annoyed ratings is `r round(nbc_tbl_tala_confint[6], 4)` with a 95% confidence interval between `r round(nbc_tbl_tala_confint[2], 4)` and `r round(nbc_tbl_tala_confint[3], 4)`. \
Conclusion: Since the estimated mean difference is negative, on average, the show 'The Apprentice: Los Angeles' has a higher annoyed rating in comparison to the show 'The Biggest Loser'. Since the confidence interval does not contain zero, the mean difference is thus statistically significant at a 5% level.

### **Part C**

```{r}

nbc_dwts <- nbc %>%
  filter(Show == "Dancing with the Stars")

nbc_dwts_bootstrap <- do(10000) * prop(~Q2_Confusing >= 4, data = resample(nbc_dwts))
nbc_dwts_confint <- confint(nbc_dwts_bootstrap, level=0.95)

```

Question: what proportion of American TV watchers would we expect to give a response of 4 or greater to the “Q2_Confusing” question?  \
Approach: In order to answer this question, I filtered the dataset to only contain observations that were from the show 'Dancing with the Stars'. Next, I computed a bootstrap of the proportion of confused ratings greater than or equal to 4 from the show. \
Results: The estimated proportion of confused ratings of 4 or greater is `r round(nbc_dwts_confint[6], 4)` with a 95% confidence interval between `r round(nbc_dwts_confint[2], 4)` and `r round(nbc_dwts_confint[3], 4)`. \

\newpage

## **Problem 4: EBay**

```{r}

boot_diff_ebay <- do(10000) * diffmean(rev_ratio ~ adwords_pause, data = mosaic::resample(ebay))
ebay_confint <- confint(boot_diff_ebay, level = 0.95)

```

Question: Is the revenue ratio the same in the treatment and control groups? Does the data favor the idea that paid search advertising on Google creates extra revenue for EBay? \
Approach: I bootstrapped the revenue ratio for the 'adwords_pause' variable in order to get the mean difference of revenue ratio between the control and treatment groups. \
Results: The estimated mean difference between revenue ratios for the control and treatment groups is `r round(ebay_confint[6], 4)` with a 95% confidence interval between `r round(ebay_confint[2], 4)` and `r round(ebay_confint[3], 4)`. \
Conclusion:  Since the estimated mean difference is negative, on average, the control group had a higher revenue ratio in comparison to the treatment group. This suggests that EBay had a higher revenue ratio with paid search advertising on Google in comparison to when advertising was paused.




